---
title: "Time Series (DA35)"
author: "Ngo Nam"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# **1.DESCRIPTION & OBJECTIVES**

The group report will begin with Time Series analysis and forecasting using the ARIMA function.

In this section, the project is done with the dataset **"Average temp in Dubuque, Iowa Jan 1964 - Dec 1975 (144)"**. The data set includes all 144 observations of monthly mean temperature in Dubuque, Iowa (January 1964 - December 1975). The raw data is preprocessed before going to the stationarity tests, selecting the optimal SARIMA function then checking residuals and finally entering the forecast.

This is the link to this part's dataset:

<https://www.york.ac.uk/depts/maths/data/ts/ts35.dat>

# **2.DATA PROCESSING**

### **IMPORT DATASET, LIBRARY & MODIFY DATASET INTO TIME SERIES FORMAT**

```{r}
library("tseries")
```

```{r}
setwd("E:/R Studio/Assignment")
da_35=read.table("ts35.dat.txt",header = FALSE)

DA35 <- ts(as.vector(t(as.matrix(da_35))),start=c(1964,1), end=c(1975,12), frequency=12)
#Describing dataset
DA35
class(DA35)
length(DA35)
summary(DA35)
```

**Plotting data**

```{r}
plot(DA35, ylab="Celsius",xlab="Year",main="Average temp in Dubuque, Iowa Jan 1964 - Dec 1975",col="blue",type="o")
plot(decompose(DA35))
acf(DA35)
pacf(DA35)
```

**We can clearly see that this series have no trend but a strong partten seasonality**

### **CHECKING IF THE DATASET IS STATIONARY OR NON-STATIONARY**

```{r}
adf.test(DA35)
```

**Differencing the series at the seasonal lag**

```{r}
diffsda35<-diff(DA35,lag=12)
#We setting lag=12 for average temp by year
plot(diffsda35,main = "Differenced TS")
acf(diffsda35,main = "Differenced TS")
pacf(diffsda35,main = "Differenced TS")
```

These shows a plot of the seasonally differenced series and its acf, pacf function. Together the plots indicate the differenced series is stationary. When taken in conjunction with the structure of the acf, we have clear evidence that a seasonal MA(1) is an appropriate model for the differenced series.The R function arima can be used to fit the full model, which is **ARIMA (0, 0, 0) × (0, 1, 1)[12]**

**Fitting process**

```{r}
#z1=arima(DA35,seas=c(2,1,0));z1
#z2=arima(DA35,seas=c(2,1,1));z2
#z3=arima(DA35,seas=c(1,1,0));z3
#z4=arima(DA35,seas=c(1,1,1));z4
#z5=arima(DA35,seas=c(0,1,0));z5
z=arima(DA35,seas=c(0,1,1));z
```

**ARIMA (0, 0, 0) × (0, 1, 1)[12]** seems to be the most appropriate model after retest base on AIC

The fitted model in this case is: $$Y_t = ε_t-ε_{t-1}$$ with $ε_t$ having an estimated variance of 11.69

### **CHECKING RESIDUALS**

Before producing forecasts of the series we need to check the residuals from the fitting process to see that they are (close to) **white noise**.

```{r fig.height=5}
tsdiag(z)
```

-   The first panel of the plot shows the (standardised) residuals from the model fit seem to be reasonably random.
-   The second panel shows the autocorrelation function for the residuals.with just one correlation lies outside the two standard error bounds
-   The third panel shows p-values for the Ljung-Box statistics at lags from one quarter to ten quarters.There is no evidence of significant correlation in this plot.

*So, the model seems to fit well.*

### **FORECASTING (1 years later)**

```{r fig.width=10}
p = predict(z, n.ahead = 12)
xlim = range(time(DA35), time(p$pred))
ylim = range(DA35, p$pred - 2 * p$se, p$pred + 2 * p$se)
plot(DA35, xlim = xlim, ylim = ylim)
lines(p$pred, lwd=2)
lines(p$pred - 2 * p$se, lty = 3, col="brown")
lines(p$pred + 2 * p$se, lty = 3,col="brown")
```

# **3.CONCLUSION**

In the graph above, we've come up with a 1-year forecast of average monthly temperatures in Dubuque, Iowa based on analysis of data from the past.

*Notably, the standard errors around forecasts widen rapidly and the forecasts themselves seem to be tending to a constant value. In fact, over the long term, forecasts for stationary series ultimately converge to the mean of the series and the standard errors for the forecasts tend to the standard deviation of the series. This means that we can only expect to gain advantage from the use of short-term forecasts.*
